---
title: "Cross-cultural similarities in pastoralists' cooperation networks are structured by kinship and social institutions"
output: 
  html_document:
    theme: readable
---

Code and data are [available on GitHub](https://github.com/matthewgthomas/hierarchies-gifts).

# Map of study sites

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(leaflet)
library(dplyr)
library(stringr)
```

```{r load_data, message=FALSE, warning=FALSE, include=FALSE}
source("init if necessary.r")

tibet = readLines("data/maqu.geojson") %>% paste(collapse="\n")
finnmark = readLines("data/finnmark.geojson") %>% paste(collapse="\n")
```

```{r labels, message=FALSE, warning=FALSE, include=FALSE}
region_sum = dyads %>% 
  # calculate per-site totals
  group_by(PopName) %>% 
  summarise(n = length(unique(Ego.ID)),
            groups = length(unique(Ego.HG)),
            gifts = sum(GiftGiven)) %>% 
  
  # keep only the region (Finnmark/Tibet)
  ungroup() %>% 
  mutate(PopName = str_split(PopName, ": ", simplify=T)[,1]) %>% 
  
  # calculate regional totals
  group_by(PopName) %>% 
  summarise_all(sum)

popup_fin = paste(sep = "<br/>", 
                  "<b>Karasjok and Kautokeino, Finnmark</b>",
                  paste0("No. herders: ", region_sum %>% filter(PopName=="Finnmark") %>% .$n),
                  paste0("No. groups: ",  region_sum %>% filter(PopName=="Finnmark") %>% .$groups),
                  paste0("No. gifts given: ", region_sum %>% filter(PopName=="Finnmark") %>% .$gifts),
                  paste0("Total area for study sites: 8831 km<sup>2</sup>"))

popup_tib = paste(sep = "<br/>", 
                  "<b>Maqu county, Gansu province, China</b>",
                  paste0("No. herders: ", region_sum %>% filter(PopName=="Tibet") %>% .$n),
                  paste0("No. groups: ",  region_sum %>% filter(PopName=="Tibet") %>% .$groups),
                  paste0("No. gifts given: ", region_sum %>% filter(PopName=="Tibet") %>% .$gifts),
                  "Total area for study sites: 10,191 km<sup>2</sup>")

lbl_style = list("color" = "black")
```

```{r areas, include=FALSE}
# calculate areas 
# (commented out because we'll just use estimates found elsewhere - see bottom of this doc for details)
#
# library(geojsonio)
# library(raster)
#
# sp_finn = geojson_read("data/finnmark.geojson", what="sp")
# finnmark_km2 = sum(area(sp_finn) / 1000000)
# 
# sp_tib = geojson_read("data/maqu.geojson", what="sp")
# tibet_km2 = area(sp_tib) / 1000000
```

```{r map, echo=FALSE, message=FALSE, warning=FALSE}
leaflet(options=leafletOptions(height=650, width=720)) %>%
  setView(lng=62, lat = 52, zoom = 2) %>% 
  addProviderTiles(providers$Esri.WorldTopoMap) %>% 
  
  addGeoJSON(finnmark, weight=2.5, color="#444444", fill=T) %>%
  addLabelOnlyMarkers(lng=25.8, lat=70, label=htmltools::HTML(popup_fin), 
                      labelOptions=labelOptions(style=lbl_style, noHide=T)) %>% 
  
  addGeoJSON(tibet, weight=2.5, color="#444444", fill=T) %>% 
  addLabelOnlyMarkers(lng=101.70, lat=33.86, label=htmltools::HTML(popup_tib), 
                      labelOptions=labelOptions(style=lbl_style, noHide=T)) %>% 
  
  addMiniMap(tiles=providers$Esri.NatGeoWorldMap, toggleDisplay=T, position="topright")
```

## Note on areas of study sites

Maqu county in China is 10,191 km^2^, according to [latitude.to](http://latitude.to/articles-by-country/cn/china/241066/maqu-county) (which seems to have gotten the figure from Wikipedia, which in turn is using an outdated link to the [International Fund for Agricultural Development](https://www.ifad.org/)).

In Norway, the district in Kautokeino covers 5,066 km^2^. Herding groups in the district in Karasjok have 3,765 km^2^ of pastures during summer and 3,752 km^2^ for the rest of the year. Data from [Ressursregnskapet for reindriftsnæringen 2015-2016](https://www.landbruksdirektoratet.no/no/reindriften/for-siidaandeler/publikasjoner).
